\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-07-28 syntax.tex
i.e. → e.g.

There are also cases we don't need to seal anything (i.e., for doing
exhaustiveness checking when using recursor), and thus \ruleref{Seal-Id} is
used.

>>>>

There are also cases we don't need to seal anything (e.g., for doing
exhaustiveness checking when using recursor), and thus \ruleref{Seal-Id} is
used.
